Applied Measure Theory for Probabilistic Modeling

### 2022-05-16 paper/paper.tex
edits

Of particular interest for the base measure is the case
\[
    \ell_\beta = \hat{\theta} \equiv \arg\max_\theta \frac{\dd\ell_\kappa(\theta)}{\dd\rho}(\ell_x)
\]

@@

An alternative parameterization of a multivariate Gaussian is in terms of its \href{https://en.wikipedia.org/wiki/Precision_(statistics)}{\emph{precision matrix}}, $\Psi = \VV[\bX]^{-1}$. Similarly to above, we'll write $\psi$ for the lower Cholesky factor of $\Psi$, so $\psi \psi^t = \Psi$. The parameterization is then specified by
\[
\bZ = \psi(\bX - \mu)\ .
\]

Solving for $z$ is of course now very simple, and the density becomes
\[
p_\bX(x) = |\psi|\ p_\bZ(z) = |\psi|\ p_\bZ(\psi (x - \mu))\ .
\]

In exchange, forward sampling becomes awkward,
\[
\bX = \psi^{-1}\bZ + \mu\ .
\]

>>>>

Of particular interest is the case where the base measure $\ell_\beta$ is
\[
    \ell_\beta = \hat{\theta} \equiv \arg\max_\theta \frac{\dd\ell_\kappa(\theta)}{\dd\rho}(\ell_x)
\]

@@

An alternative parameterization of a multivariate Gaussian is in terms of its \href{https://en.wikipedia.org/wiki/Precision_(statistics)}{\emph{precision matrix}}, $\Lambda = \VV[\bX]^{-1}$. Similarly to above, we'll write $\lambda$ for the lower Cholesky factor of $\Lambda$, so $\lambda \lambda^t = \Lambda$. The parameterization is then specified by
\[
\bZ = \lambda(\bX - \mu)\ .
\]

In this parameterization, $\lambda$ is an \emph{inverse scale} or \emph{rate} parameter.
Solving for $z$ is of course now very simple, and the density becomes
\[
p_\bX(x) = |\lambda|\ p_\bZ(z) = |\lambda|\ p_\bZ(\lambda (x - \mu))\ .
\]

In exchange, forward sampling becomes awkward,
\[
\bX = \lambda^{-1}\bZ + \mu\ .
\]
